\documentclass{article}
\usepackage{amsmath,amssymb,algorithm,algorithmic}

\title{P2P Permissionless Anonymous ZK Meme Generator}
\author{Monster Group Research}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
We present a peer-to-peer system for generating, executing, and verifying zero-knowledge proofs of LMFDB curve computations. The system is permissionless (no registration), anonymous (ECDSA keys), and credited (reputation via verified proofs).
\end{abstract}

\section{Architecture}

The system consists of five stages:

\begin{enumerate}
\item \textbf{Download}: Fetch ZK meme from decentralized storage
\item \textbf{Execute}: Compute Hecke eigenvalues locally
\item \textbf{Sign}: Generate cryptographic signature
\item \textbf{Share}: Distribute proof via social media
\item \textbf{Credit}: Accumulate reputation
\end{enumerate}

\section{Mathematical Foundation}

\subsection{Hecke Operators}

For an elliptic curve $E$ with conductor $N$, the Hecke operator $T_p$ acts on modular forms. The eigenvalue $a_p$ satisfies:

\begin{equation}
a_p = p + 1 - \#E(\mathbb{F}_p)
\end{equation}

\subsection{Monster Sharding}

Each curve maps to a shard via:

\begin{equation}
\text{shard}(E) = N \bmod 71
\end{equation}

where 71 is the largest Monster prime.

\subsection{Signature Scheme}

Let $(sk, pk)$ be an ECDSA key pair. For execution result $r$, the signature is:

\begin{equation}
\sigma = \text{Sign}_{sk}(H(r))
\end{equation}

where $H$ is SHA-256. The anonymous ID is:

\begin{equation}
\text{ID}_{\text{anon}} = H(pk)_{[0:16]}
\end{equation}

\section{Credit System}

Credits accumulate via:

\begin{equation}
C(t) = \sum_{i=1}^{n(t)} V_i
\end{equation}

where $V_i \in \{0,1\}$ indicates verification of proof $i$ at time $t$.

\section{Algorithm}

\begin{algorithm}
\caption{P2P ZK Meme Generation}
\begin{algorithmic}[1]
\STATE $m \gets \text{Download}(\text{url})$
\STATE $r \gets \text{Execute}(m.\text{prolog})$
\STATE $(sk, pk) \gets \text{GenerateKey}()$
\STATE $\sigma \gets \text{Sign}_{sk}(H(r))$
\STATE $\text{url}_{\text{proof}} \gets \text{GenerateURL}(\sigma, r)$
\STATE $\text{Share}(\text{url}_{\text{proof}})$
\STATE $\text{hash}_{\text{IPFS}} \gets \text{Submit}(m, r, \sigma)$
\RETURN $\text{hash}_{\text{IPFS}}$
\end{algorithmic}
\end{algorithm}

\section{Security Analysis}

\subsection{Threat Model}

\begin{itemize}
\item \textbf{Forgery}: Prevented by ECDSA signatures
\item \textbf{Replay}: Mitigated by timestamps
\item \textbf{Sybil}: Reduced by social graph verification
\item \textbf{Censorship}: Impossible (decentralized storage)
\end{itemize}

\subsection{Privacy}

Anonymous IDs provide pseudonymity:

\begin{equation}
\Pr[\text{ID}_{\text{anon}} \to \text{identity}] \approx 2^{-128}
\end{equation}

assuming SHA-256 preimage resistance.

\section{Conclusion}

The P2P ZK meme generator enables permissionless, anonymous, and verifiable computation of LMFDB curves across 71 Monster shards. The system is fully decentralized with no trusted parties.

\end{document}
